\section{Planning}\label{sec:planning}
The initial schedule for the project can be seen in table \ref{tab:schedule}. It is to be mentioned, that the schedule is subject to change as the project goes on. The project will be executed in a scrum-like way that is adapted to the group, given the group size of two developers.
\begin{table}[htbp]
\centering
\large
\resizebox{1\textwidth}{!} {
\begin{tabular}{|c"cc:cccc:cc:ccccccccc:ccc:c|} \hline
\textbf{Sprints} & \multicolumn{2}{>{\centering\arraybackslash} m{.15\textwidth}|}{\textbf{Logistics Processes \& Wearables}} & \multicolumn{4}{>{\centering\arraybackslash} m{.35\textwidth}|}{\textbf{Reference Architecture}} & \multicolumn{2}{>{\centering\arraybackslash} m{.25\textwidth}|}{\textbf{Research Demo Facility}} & \multicolumn{9}{c|}{\textbf{Demo Facility Design and Implementation}}                   & \multicolumn{3}{>{\centering\arraybackslash} m{.25\textwidth}|}{\textbf{Creation Demo Facility}} & \multicolumn{1}{>{\centering\arraybackslash} m{.08\textwidth}|}{\textbf{Buf-fer}} \\ \thickhline
Date                 & 06.02              & 13.02              & 20.02                & 27.02                & 06.03         & 13.03        & 20.03        & 27.03 & 03.04 & 10.04 & 17.04 & 24.04 & 01.05 & 08.05 & 15.05 & 22.05 & 29.05 & 05.06         & 12.06        & 19.06        & 26.06                             \\
Week                       & 6                  & 7                  & 8                    & 9                    & 10            & 11           & 12           & 13    & 14    & 15    & 16    & 17    & 18    & 19    & 20    & 21    & 22    & 23            & 24           & 25           & 26 \\\hline       	              
\end{tabular}
}
\caption{Schedule}
\label{tab:schedule}
\end{table}

The schedule is divided in work packages that are to be executed, it is to be noted, that each work package could be split into multiple sprints in the future. In the following subsections the work packages will be explained.

\subsection{Logistics Processes \& Wearables}
This work package includes research about the gives processes and wearables in general, as well as already choosing potential wearables that could be used to improve the process. The end result for this should be a decision on process and wearable. But the result for this could potentially take longer than this task is scheduled. The wearables should be ranked after getting hands-on experience on them, therefore some of them have to be ordered first.

\subsection{Reference Architecture}
A reference architecture should be created for a sample wearable application. What this work package contains is, the creation of diagrams which show the communication from a wearable to the \gls{wms} or something similar. What should not be created is a full reference architecture for a process that is implemented with a concrete wearable. 

It is about creating the always needed layers when using a wearable in a way that supports most wearable solutions.

\subsection{Research Demo Facility}
This task includes researching what physical objects and what systems would be needed to create a demo facility that could showcase a single process with a single wearable. This also includes the gathering of knowledge of where the demo facility should be created and where to get the needed objects.

\subsection{Demo Facility Design and Implementation}
The work package includes the creation of the software design and implementation for the wearable and all aspects that are needed to fully showcase a process.

\subsection{Creation Demo Facility}
This task includes the physical creation of the demo facility. This means setting up shelves with packages to scan and put on a hand pallet truck. Setting up barcodes on the packages to scan. Setting up an environment that can showcase what is happening better to an audience.
