\chapter{Research}\label{cha:research}
This chapter includes the general research that has been done for the project. Which includes the research about some given processes and wearables that could be appropriate for the processes. The CASE Tools chosen at the current state of the project will also be discussed and what they are used for.

\section{Processes}\label{sec:processes}
There were process already modelled and made available in the LOGwear project. The given processes were:

\begin{itemize}
	\item Order Picking High Rack
	\item Order Picking W3-5
	\item Goods Receipt and Put away
\end{itemize}

Those three processes can also be found in \ref{appendix}.

Order Picking High Rack has been discarded due to the nature of what should be created. A simulation that should model a real environment. Modelling a High Rack and usage of that would be too hard and would take too much time.

Goods Receipt and Put away was another process to be considered, but was discarded. The modelling of it would be problematic due to the time delays in the tasks. Furthermore the process showed less potential for improvements with wearables.

Order Picking W3-5 was the process chosen to improve with wearables as multiple possibilities to improve the process were discovered. Also the processes seemed rather easy to model with a demo facility by setting up one or two racks and placing multiple packages on there.

The process has been decided together with the company supervisor.

\section{Wearables}\label{sec:wearables}
Researching wearables was a more problematic task, as the amount of wearables that could be used potentially is a lot higher. Some criteria were set in place for a wearable to be considered in the first place. A wearable has to be either already available, or freely available to order in europe from a trusted source. This leads to well known wearables like the Google Glass to be not even considered as they are not publicly available.


\section{CASE Tools}\label{sec:caseTools}
The \gls{case} tools chose here are only for the parts already decided on. As a chosen wearable could introduce a lot more \gls{case} tools to the project. 